---
title: "Motor Trend Car Road Analysis"
output: word_document
---
###Brief
View the report at the following link: https://rpubs.com/pipinho13/124740

Motor Trend is a magazine about the automobile industry and they are interested in exploring the relationship between a set of variables and miles per gallon. 
They are particularly interested in the following two questions:

“Is an automatic or manual transmission better for MPG” 

"Quantify the MPG difference between automatic and manual transmissions"

###Summary

For this analysis we considered the dataset of mtcars. The initial aim is to find if there is a relationship between MPG and transmissions and also 
to try to build a regression model in order to quantify the MPG difference between automatic and manual transmissions. Finally in order to come up with
the most appropriate model we examine also other variables and we kept also the most statistical significant using the "stepwise" process.


###Data Analysis


Libraries used

```{r, message=F, warning=F }
library(ggplot2)
library(MASS)
```

###Exploratory Analysis


```{r}
str(mtcars)
```

A boxplot shows that the Manual Transmission has higher MPG than the Automatic
```{r}
qplot(factor(mtcars$am, labels = c("Automatic", "Manual")), mtcars$mpg, data=mtcars, geom="boxplot", xlab='Transmission', ylab='Miles per Gallon', main='Miles/Gallon per Transmission')
```

Also a T-test confirms that there is statistical difference in Transmission regarding the MPG (P-Value<0.05)

```{r}
t.test(mtcars$mpg~mtcars$am,conf.level=0.95)
```

###Regression Analysis



###Stepwise Regression

At this point we are going to run a regression model using al the variales and by applying the stepwise algorith we are going to keep the 
most appropriate variables

```{r}
stepwisemodel = step(lm(data = mtcars, mpg ~ .), trace=0, direction=c("both"))
summary(stepwisemodel)
```
The model suggests that we should keep the variables wt, qsec and am in order to explain the MPG. 
Explanation of the coefficient variables

Every lb/1000 weight increase will cause a decrease of roughly 3.9 MPG

Every increase of 1/4 mile time will cause an increase of 1.2 MPG, and on average, 

On average a manual transmission leads to 2.93 more MPG than the automatic

The model is able to explain 85% of variance and the residual plots shows to be distributed normally 


###Conclusion

The MPG can be explained by the "weight" the "mile time" and the "transmission". However maybe there exist other factors who can explain better the MPG.


The plot below shows the data that we have chosen in order to explain the MPG

```{r}
mtcars$amf <- factor(mtcars$am, labels = c("Automatic", "Manual"))
qplot(wt, mpg, data=mtcars, col=amf, size=qsec)
```

###Appendix

A pairwise scatter plot can help us to see the correlation between all the variables 

```{r}
pairs(mtcars)
```

And the residual plots of the final suggested model
```{r}
par(mfrow=c(2,2))
plot(stepwisemodel)
```
